### 2020-05-13 writeup/proof_transfer_ex.tex
sec 3.1

@@

\begin{lemma}
	Recall that $\hat{v} = \hat{w_1} / \hat{w_2}$.
	In the setting of Proposition \ref{prop_dist_transition}, we have that
	\[ \abs{\hat{v} - 1} \le o(1). \]
\end{lemma}

Since $\Sigma_1 = \Sigma_2$, we know that $M = \hat{v}\Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
\begin{align}
	\Delta_{\vari} \define \sigma^2 \bigbrace{ - \frac{1}{c_2 - 1}},
\end{align}
where we solve equation \eqref{eq_a12} to obtain $a_1 = $ and $a_2 = $.

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, upper bound]
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, lower bound]
\end{proof}

Hence the task models have distance $d^2\cdot p$ in expectation.
	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
	\begin{align} \label{eq_delta_simple}
		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
	\end{align}
	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
	\begin{align}
		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
	\end{align}
%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
%	\begin{align}
%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
%	\end{align}
%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
%}

	Then we obtain
	\begin{align}
		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
	\end{align}

>>>>

Finally, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
\todo{restate this}
\begin{lemma}\label{prop_model_shift_tight}
		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
		and we have
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
		\end{align*}
\end{lemma}

@@

\begin{lemma}\label{lem_hat_v}
	Recall that $\hat{v} = \hat{w_1} / \hat{w_2}$.
	In the setting of Proposition \ref{prop_dist_transition}, we have that
	\[ \abs{\hat{v} - 1} \lesssim \frac 1 p. \]
\end{lemma}

Based on Lemma \ref{lem_hat_v}, we can prove Proposition \ref{prop_dist_transition}.
\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	Since $\Sigma_1 = \Sigma_2$, we know that $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
	Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as whp
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{c_2 - 1} - \frac{1}{c_1 + c_2}\cdot\frac{1}{a_1\hat{v}^2 + a_2} + \bigo{p^{-1/2+\varepsilon}}} \\
		&= \sigma^2 \bigbrace{\frac{c_1}{(c_2-1)(c_1 + c_2 -1)} + \bigo{p^{-1/2 + \varepsilon}}},
	\end{align*}
	where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next we consider the model shift bias
	\begin{align*}
		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}}
	\end{align*}
	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
	\[ \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{\frac 1 p} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \]
	By solving equations \eqref{eq_a12}, \eqref{eq_a3} and \eqref{eq_a4}, we get
	\begin{align*}
		& a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}),
		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}), \\
		& a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}),
		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}).
	\end{align*}
	Hence we obtain that
	\begin{align*}
		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
	\end{align*}
	To sum up, we have shown that when
	\[ \frac{p\cdot d^2}{\sigma^2} < \frac{(c_1 + c_2 - 1)^2}{c_1(c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 + \sqrt{\frac 1 {c_1}}}^{-4}, \]
	we have that $\Delta_{\vari} > \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$.
	When
	\[ \frac{p\cdot d^2}{\sigma^2} > \frac{(c_1 + c_2 - 1)^2}{c_1 (c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 - \sqrt{\frac 1 {c_1}}}^{-4}, \]
	we have that $\Delta_{\vari} < \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is higher than $\te(\hat{\beta}_t^{\STL})$.
	The result follows by taking $c_1 = c_2 = c$ for the above equation.
\end{proof}

### 2020-05-13 writeup/transfer.tex
sec 3.1

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the example described above, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac{2(2c-1)^2}{(c-1)(2c+1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{2(2c-1)^2}{(c-1)(2c+1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

>>>>

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the example described above, assume that $c > 50$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac 1 4 \frac{(2c-1)^2}{(c-1)c^2} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{(2c-1)^2}{(c-1)c^2} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
